Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-12-25 cogsci/cogsci.tex
new changes

\usepackage[subtle]{savetrees}

@@

How do children acquire words? An important step consists in mapping a
phonological form (e.g.~the sound ``cat'') to a semantic referent (the
concept CAT). A large body of work has been devoted to explore the
mechanism of this mapping (Quine, 1960; Markman, 1990; Smith and Yu,
2008). However, words do not exist in a vacuum; they are organized into
a strcuture based on both semantic and phonological similarity
principles (e.g., Collins \& Loftus, 1975; Luce \& Pisoni, 1998). A more
accurate understanding of word learning should account not only for how
sounds are mapped to meanings, but also for how sound similarity and
meaning similarity may influence the process of aqusition.

We know that similarity affect word recognition in both adults and
children. For example, exposure to a word such as ``cat'' influences
subsequent recognition of phonologically and smantically similar words
like ``cab'' and ``dog'' (Goldinger, Luce \& Pisoni, 1989; McNamara,
2006; Arias-Trejo \& Plunkett, 2010; Mani \& Plunkett, 2011).

Crucially, similarity influences not only the recognition of know words,
but also the learning of novel words. For example, Swingley \& Aslin
(2007) showed that infants found it more challenging to learn the
meaning of a novel word such as ``tog'' (which is similar a the familiar
word ``dog'') than to learn the meaning of a word such as ``shang''
(which is not similar to any words children knew). When learning two
novel words, Stager and Werker (1997) found that infatns were more
likely to succeed when these words were phonologically distant (e.g.,
``lif''/``neem''), than when they were phonologcially simialr
(``bin/''din``). Besides, children learn the semantic relationship among
newly learned words spontaneousely (Wojcik \& Saffran, 2013), and they
prioritize the acquisition of words that are distinct in the semantic
space (Engelthaler \& Hills, 2017).

That said, previous experimental work has studied the effect of
phonological and semantic similarity separately. Some studied the
mechanism of word learning using a toy lexicon where only the
phonological similarity varied (e.g., Stager and Werker, 1997), and
others studied the learning of a toy lexicon where only the semantic
similarity varied (e.g., Wojcik \& Saffran, 2013). However, children
acquire a lexicon which is more richly structured than these special
cases. In particular, as reviewed abvove, the end-state lexicon involves
variability along both the phonological and semantic domains. Thus, to
have a deeper understanding of word acquisition in the real world, it is
crucial to study how learners acquire a lexicon that simulates this
bi-dimensional variation.

One could imagine two learning scenarios. On the first one, children's
learning, at least in some challenging situations, is primarily
determined by one dimension (Sloutsky \& Napolitano, 2003; Colavita et
al. 1975). For example, it is possible that similar sounding words are
confusable and hard to learn regardless of their semantic similarity.
Vice-versa, similar meanings might be challenging to learn regardless of
the phonological similarity of their forms. On the second scenario,
learners combine cues from both dimensions to optimize their learning
(Fourtassi and Frank, 2018; Ernst \& Banks, 2002). Thus, confusability
that may arise from high similarity along one dimension can be mitigated
via higher distance from the other dimension. In this study, we explore
these hypothesis, bla bla

A second goal of this work is to investigate how the learning mechanism
develops over the life span. According to one hypothesis, adults use
qualitatively distinct learning mechanisms than children, due, for
example, to maturational factors. To illustrate, in the experimental
setting used in Stager and Werker (1997), children's difficulty with
learning similar sounding words--despite their ability to perceptually
differentiate them--might be attributed to their inferior working
memory, hindering their ability to attend simultaneously to the sound
contrast and the meanings. A second hypothesis proposes that learners
use fundamentally similar mechanisms across the life span, and that the
difference might be one of degree, not kind. For example, though they
have vastly greater working memory capacity, adults show patterns of
word processing and learning which parallel results obtained with
children in Stager and Werker's study (White et al. 2013; Pajak et al.
2016). Here we explore

Talk a bit about what we do

\section{Experiment 1}\label{experiment-1}

Children were trained to learn the association between pairs of
nonesense words (e.g., ``lif''/``neem'') and pairs of objects (e.g., two
flowers). After training, children performed a series of two-alternative
forced choices. In each testing trial, one of the two sounds is uttered
(e.g., ``lif'') and participants choose the corresponding object from
the two alternatives (e.g., flower 1 or flower 2). Each child learned an
artificial lexicon where both the pairs of sounds and the pairs of
objects can be similar or different. Our predictions were as follows. If
the sound and meaning interact in word learning, then the pair of words
that differ on both the meaning and sound levels should be the easiest
to learn, followed by the pairs of words that are different on one
level, but similar on another level. Finally, the pair of words that are
similar on both levels should be the most difficult to learn.

We planned to recruit a sample of 60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. So far, we
collected data from N=47 children (mean age= months, F=). An additional
28 children participated but were removed from analyses because they
were not above chance on the catch trials (as specified in the
pre-registration).

\subsubsection{Stimuli}\label{stimuli}

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Cite) using an American English voice. We generated two similar sound
pairs (``aka''/``ama'' and ``ada''/``aba'') and two different sound
pairs (``lif''/``neem'' and ``zem''/``doof''). We generated a addtional
pair (``nak''/``veep'') which we used in the catch trial (see
Procedure). As for the objects used as semantic referents, we used the
Dynamic Categories Stimuli (Cite) which allowed us to generate objects
in four different categories: ``tree'', ``bird'', ``bug'', and ``fish''
(plus the additional category ``flower'' for the catch trial). These
categories are supposed to be naturally occuring kinds that might be
seen on an alien planet. In each category, we generated instances that
varied in their similarity by manipuating a continuous property
controling features of the category's shape. This property was the head
fatness for the category ``bug'', the body strech for ``bird'', the tail
size relative to the body fatness for ``fish'', the width of the trunk
for ``tree'', and finally center size for ``flower''. All these
continous properties varied on a scale from 0 to 1. We generated
``similar'' and ``different'' objects' pairs (whithin each category) by
setting the values of this properties to 0 and 0.5, and to 0 and 1,
respectively. Examples of the resuting pairs are shown in Figure XX.

The experiment consisted of 4 conditions which consisted, each, of a
pair of sounds-objects associations. These conditions were constructed
by crossing the sound's degree of similarity with the object's degree of
similarity leading to a 2x2 factorial design. Besides the 4 conditions,
we also tested participants on a fifth catch condition which was similar
to the previous ones. It involved different sounds and different
objects, and it was used only to select participant who were able to
follow the instructions and show minimal learning (not at chance level).

Children were asked if they would be willing to play a game on a tablet
with the experimenter and were informed that they could stop playing at
any time. The experimenter explained that the game consisted in learning
some words spoken in an alien planet. The experiment began with two
simple examples (not included in the analysis), and in these examples
children were given feedback from the experimenter so as to make sure
they correctly understood the structure of the task. After the
introduction and examples, children were tested in a sequence of five
conditions: the four experimental conditions plus the catch condition.
In each condition, participants saw a first block of four exposure
trials followed by four testing trials, and a second block of two
exposure trials (for memory refreshment) follwoed by an additional four
testing trials.

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial. The experiment can be views online using this link XX.

\subsubsection{Results}\label{results}

@@

\caption{\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
\end{figure}
\end{CodeChunk}

Studies that investigate lexical network growth have focused on semantic
networks using English data (Hills, Maouene, Riordan, \& Smith, 2010;
Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Steyvers \& Tenenbaum,
2005). The novelty of the current study is threefold: First, it
investigates whether phonological networks, like semantic networks, grow
by PAC, or if they rather grow by PAT. Second, it provides a systematic
comparison of both network growth scenarios in the phonological and the
semantic domains and assesses their relative contribution to the
learning process. Third, it tests the generality of the findings across
eight languages.

@@

{\centering \includegraphics{figs/degree_distribution-1}

\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
\end{figure*}
\end{CodeChunk}

\section{Networks}\label{networks}

\subsection{Data}\label{data}

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). We used the
\emph{Words and Sentences} version of the CDI which contains the
productive vocabulary of toddlers (age varied between 16 to 36 months).
Following previous studies (Hills et al., 2009; Storkel, 2009), we
restricted our analysis to nouns. We defined the age of acquisition of a
given word by the month at which this word was produced by at least 50\%
of children (J. C. Goodman, Dale, \& Li, 2008), and we excluded nouns
that have not been learned (according to this criterion) by the last
month for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English,
Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
nouns that had entries in the Florida Association Norms (see below).
Since these norms are available only in English, we used the
hand-checked translation equivalents provided by Braginsky, Yurovsky,
Marchman, \& Frank (2016), allowing us to use the English association
norms across languages. Table \ref{tab:stats} gives an overview of the
data used. Translation equivalents were originally constructed for a
subset of words appearing on the toddler CDI form, and so not all words
are currently available. Note, however, that all languages have at least
60\% of nouns translated.

\begin{table}[H]
\centering
\begin{tabular}{rlrrr}
  \hline
 & language & total & translated & normed \\ 
  \hline
1 & Croatian & 253 & 177 & 170 \\ 
  2 & Danish & 295 & 198 & 187 \\ 
  3 & English & 296 & 296 & 274 \\ 
  4 & Italian & 311 & 203 & 194 \\ 
  5 & Norwegian & 305 & 193 & 186 \\ 
  6 & Russian & 311 & 311 & 285 \\ 
  7 & Spanish & 240 & 173 & 163 \\ 
  8 & Turkish & 293 & 175 & 164 \\ 
   \hline
\end{tabular}
\caption{\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left). We included in our study the subset of these nouns that had available English translations (middle). The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).} 
\end{table}

\subsection{Semantic networks}\label{semantic-networks}

We constructed semantic networks following the procedure outlined in
Hills et al. (2009). We used as an index of semantic relatedness the
Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
This dataset was collected by giving adult participants a word (the
cue), and asking them to write the first word that comes to mind (the
target). For example, when given the word ``ball'', they might answer
with the word ``game''. A pair of nodes were connected by a directed
link from the cue to the target if there was a cue-target relationship
between these nodes in the association norms. The connectivity of a
given node was characterized by its \emph{indegree}: the number of links
for which the word was the target. To model growth from month to month,
we constructed a different network at each month, based on the words
that have been acquired by that month.

\subsection{Phonological networks}\label{phonological-networks}

We generated approximate International Phonetic Alphabet (IPA)
transcriptions from the orthographic transcription, across languages,
using the open source text-to-speech software
\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
the Levenshtein distance (also known as edit distance) as a measure of
phonological relatedness between two nodes. The measure counts the
minimum number of operations (insertions, deletions, substitutions)
required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance
of 1 (e.g., Storkel, 2009). However, in these previous studies the
network was built using an adult vocabulary. In the current study,
however, network growth models are based on the children's early
vocabulary which contains very few word pairs with an edit distance of
1. When using this threshold, the resulting networks were too sparse and
uninformative. Thus, we increased the threshold from 1 to 2, that is,
two nodes were related if their edit distance was equal to 1 or 2. The
connectivity of a given node was characterized with its \emph{degree}:
the number of links it shares with other words.

\section{Analysis}\label{analysis}

\subsection{Static properties of the global
network}\label{static-properties-of-the-global-network}

We start by analyzing word connectivity in the global (static) network.
We constructed this network using nouns learned by the oldest age for
which we have CDI data (e.g., in English this corresponds to the network
by 30 months). This global network is the end-state towards which both
PAT and PAC should converge by the last month of learning. Moreover,
following Hills et al. (2009), we used this end-state network as a proxy
for the external connectivity in the learning environment. Below we
analyze properties of this global networks that are relevant to PAC
and/or PAT.

\subsubsection{Connectivity predicts the age of
acquisition}\label{connectivity-predicts-the-age-of-acquisition}

Connectivity in the global network is directly related to PAC as it
represents the explicit criterion PAC uses to determine what words
should be learned first (Figure \ref{fig:growth}). Therefore, a direct
consequence of a PAC-like growth scenario is a correlation between
connectivity in the global network and the age of
acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
Figure \ref{fig:data_all} shows how the age of acquisition for each word
varies as a function of its degree (or indegree for the semantic
network). For ease of visual comparison, the predictor (i.e., the
degree) was centered and scaled across languages. The plots show,
overall, a negative correlation between the month of acquisition and the
degree, indicating that nouns with higher degrees are generally learned
earlier.

\subsubsection{Power-law degree
distribution?}\label{power-law-degree-distribution}

We also analyzed the global network's degree distribution. The shape of
this distribution is particularly relevant to PAT as this growth
scenario is known to generate networks with a power-law degree
distribution (i.e., a distribution of the form
\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
network displays this property, this fact would suggest a PAT-like
generative process. Conversely, if the degree distribution does not
follow a power law, this fact would weaken the case for PAT. The log-log
plots are shown in Figure \ref{fig:degree_distribution}. We fit a power
law to each empirical degree distribution following the procedure
outlined in Clauset, Shalizi, \& Newman (2009) and using the related R
package (poweRlaw, Gillespie, 2015). In brief, the analysis consisted in
two steps. First, we derived the optimal cut-off, \(k_{min}\), above
which the distribution is more likely to follow a power
law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
and we estimate the corresponding scaling parameter \(\alpha\). Second
we calculated the goodness-to-fit, which resulted in a \(p\)-value
quantifying the plausibility of the model. Overall, we could not reject
the null hypothesis of a power-law distribution: the \(p\)-value was
generally above 0.1, except for the Italian phonological network where
we obtained \(p < 0.05\), suggesting that the power law can be ruled out
in this particular case.

In sum, the static properties of the global network are \emph{a priori}
compatible with both PAT and PAC. In order to decide between these two
developmental scenarios, we need to fit explicit growth models to the
data.

{\centering \includegraphics{figs/pred_ind_img-1}

\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:pred_ind_img}
\end{figure*}
\end{CodeChunk}

\subsection{Network growth models}\label{network-growth-models}

\subsubsection{How does each growth scenario predict noun
development?}\label{how-does-each-growth-scenario-predict-noun-development}

To test the network growth scenarios, we fit different growth models to
the data. We calculated the probability that a word \(w_i\), with a
growth value \(d_i\) would enter the lexicon at a given month, using a
softmax function:

\begin{equation}
 p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
\end{equation}

\noindent where \(\beta\) is a fitted parameter that captures the
magnitude of the relationship between network parameters and growth
(analogous to a regression coefficient). A positive value of \(\beta\)
means that words with higher growth values \(d_i\) are acquired first,
and a negative value means that words with lower growth values are
acquired first (see Figure \ref{fig:growth} for an illustration of how
growth values \(d_i\) are defined in each growth scenario). The
normalization includes all words that could be learned at that month.

We estimated the parameter \(\beta\) using a Bayesian approach. The
inference was performed using the probabilistic programming language
WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
over \(\beta\), and at each month, we computed the likelihood function
over words that could possibly enter the lexicon at that month, fit to
the words that have been learned at that month (using formula 1). Markov
Chain Monte Carlo sampling resulted in a posterior distribution over
\(\beta\), which we summarized in Figure \ref{fig:pred_ind}.

For the semantic networks, the results replicate Hills et al.'s finding
in English, which is that the semantic network grows by PAC, not by PAT.
Moreover, this finding holds in seven of the eight languages we
examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.}
The PAC model also fits better than PAT for phonological networks. We
note however that PAT, though weaker, fares better for the phonological
networks (where it predicts part of the growth process in some languages
such as Croatian, English, Norwegian and Russian) than it does for the
semantic networks (where it is rather universally unpredictive).

\subsubsection{What is the relative contribution of each growth
model?}\label{what-is-the-relative-contribution-of-each-growth-model}

Above we evaluated the network growth scenarios individually. As a next
step, we analyzed their relative contribution to the learning process.
This was done through adding more fitted parameters to the model, that
is, by substituting \(\beta d_i\) in formula (1) with:
\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
PhonoPAC. Using the same fitting technique, we obtained the values shown
in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
phonological and semantic networks contribute to lexical growth, but the
phonological network appears to be stronger and more consistent across
languages. In summary, the findings show that both semantic and
phonological networks contribute to the learning process, and that they
both grow primarily by PAC, relying on the external connectivity in the
learning environment, rather than the internal connectivity in the
acquired lexicon.

{\centering \includegraphics{figs/regressions_img-1}

\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:regressions_img}
\end{figure*}
\end{CodeChunk}

\subsection{Comparison to other predictors of age of
acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}

We saw that the way semantic and phonological information is structured
in the learning environment (i.e., PAC) contributes to noun learning
across languages. However, we know that other factors influence learning
as well (e.g., Braginsky et al., 2016). Next we investigated how
semantic and phonological connectivity interact with two other factors.
The first one is word frequency, a well studied factor shown to predict
the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
2008). The second factor is word length, which correlates with
phonological connectivity.

Since PAT was uninformative, we dropped it from this analysis, keeping
only PAC. This simplified the model because we no longer needed to fit
growth
month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.}
A more direct way to assess and compare the contribution of PAC in
relation to other word-level factors is through conducting linear
regressions, where connectivity in the learning environment, frequency
and length predict the age of acquisition.

We used the frequency estimates from Braginsky et al. (2016) where
unigram counts were derived based on CHILDES corpora in each
language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
For each word, counts included words that shared the same stem (e.g.,
``cats'' counts as ``cat''), or words that were synonymous (e.g.
``father'' counts as ``daddy''). For word length, we counted the number
of phonemes in our generated IPA transcription.

>>>>

\usepackage[subtle]{savetrees}
\usepackage{tipa}

@@

Over the first year of life, children become sensitive to the phonetic
variations that are used to distinguish meanings in their native
language (Werker and Tees, 1984). One could imagine that these
perceptual skills would be automatically applied to the task of word
learning. However, developmental data show that 14 m.o children find it
challenging to associate minimally different (but perceptually
discriminated) sounds such as ``bin'' and ``din'' to different objects
(Stager \& Werker, 1997).

Several factors can explain this pattern of results. For example it is
possible that the task of meaning learning increases cognitive demands
on children (compared to a simple perceptual descrimination). In
particular, it requires paying attention to both the sounds and the
corresponding objects, which may hinder precise encoding in memory of
some phonetic details (Stager a\& Werker, 1997). Additional difficulty
might arise from ambiguous phonological boundaries at this stage of
development (e.g., Rost \& McMurray, 2009), or from uncertainty about
the referential status of the novel word (Fennell \& Waxman, 2009).

Regardless of the exact explanation, it is generally accepted that by
around 17 m.o, chidlren succeed under the same circumstances (Werker et
al. 2002). What could be the mechanism of development? Swingley
contrasted a binary-discontinuous scenario to a probabilstic-continuous
one. On the discontinuous account, younger children learn a single,
underspecified representation of similar words (e.g., ``bin''/``din'').
Development occurs when children specify this intial coarse
reprepsentation and learn two distinct catgories. On the continuous
account, distinct represetations are successfully learned from the
start, but these representations are encoded with higher uncertainty in
youger children, leading to apparent failure in relatively demanding
tasks.

Experimental evidence suggest a probabilsitic-continuous, rather than a
stage-like develomental scenario. On the one hand, 14-month-olds who
typically fail in the original task succeed when learning is probed
using a testing method with lower memory demands (Yoshida et al. 1009),
and when uncertainty in the emerging representations is mitigated using
disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016).
On the other hand, adults show patterns of learning similar to those
shown by 14-month-olds when the task is more challenging and when
similarity between words increases (Pajak et al., 2016; White et al.,
2013).

Following this experimental studies, the purpose of the current work is
to propose a precise probabilsitc model of the Stager and Werker's task,
and to explore the extent to which such a model could provide a unified
accounts for several documented (as well as new) patterns of learning
and development. We first present the model and explain how it can be
used to make precise predictions of the target behavioral responses.
Second, using new data collected from both preschool children and
adults, we show how the probabilistic strucure of the model can explain
behavioral patterns both within the same age and across development.

@@

\caption{\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.  }\label{fig:growth}
\end{figure}
\end{CodeChunk}

\section{Model}\label{model}

\subsection{Task}\label{task}

We model a variant of the task used in Yoshida et al. 2009. In this
task, particiants are first exposed to the association between pairs of
nonesense words (e.g., ``lif''/``neem'') and pairs of objects. After
this exposure phase, participants perform a series of two-alternative
forced choices. In each testing trial, one of the two sounds is uttered
(e.g., ``lif'') and participants choose the corresponding object from
the two alternatives.

\subsection{Probabilistic strcuture}\label{probabilistic-strcuture}

Our model consists of a set of variables describing the general process
of spoken word recognition in a referential situation. These variables
are related in a way that refelects the simple generative scenario
represented graphically in Figure XX. When a speaker utters a sound in
the presence of an object, the observer assumes that the object \(o\)
activated the concept \(C\) in the speaker's mind. The concept prompted
the cooresponding label \(L\). Finally, the label was physically
instantiated by the sound \(s\).

{\centering \includegraphics{figs/model-1}

\caption{\label{fig:model}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters.}\label{fig:model}
\end{figure}
\end{CodeChunk}

Because of the noisy nature of the representations, the observer can
only determine the hidden variables (i.e., the concept \(C\) and the
label \(L\)) in a probabilistic fashion. For simplicity, we assume that
the probability of membership of objects and sounds to concepts and
labels, respectivel, are normally distributed:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
one-to-one mappings between concepts and labels, and that observers have
successfully learned these mappings during the exposure phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
\] \#\# Predictions

During the testing phase (see Figure 1), participants are presented with
one target sound \(s_T \in\{s_1, s_2\}\) and two possible objects
\(o_1\) and \(o_2\). In order to make a choice, we determine which
object is more probable under the lable \(s_T\), in other words, we
compare the the probabilities \(P(o_1|s_T)\) and \(P(o_2|s_T)\). The
values of these probabilities can be computed by summing over all
possible labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
The joint probability \(P(o, C, L, s)\) is obtained by factoring the
bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
which could be tansformed using Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
concept prior is a uniform ditribution, we obtain the following
expression, where all conditional dependencies have been defined in the
previous secton.

\begin{equation}
P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
\end{equation}

From the general expression (1) we were able to derive the exact
analytical expression of the probability of correct responses in the
testing phase of our simplified experimenal setting (Figure 1).

\begin{equation}
P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
\end{equation}

We simulate the values of this probability as a function of the
perceptual distance between the sounds \(\Delta s\), using the two
remining parameters of the model: the visual distance between the
semantic referents \(\Delta o\) and the values of the standard deviation
of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
simulation, have similar values, i.e.,
\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
Figure 3.

{\centering \includegraphics{figs/simulation-1}

\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits.}\label{fig:simulation}
\end{figure*}
\end{CodeChunk}

The simulations explain previousely documented facts, and make new
predictions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
  accurate responses increases as a function of \(\Delta s\). This
  pattern accounts for the fact that similar sounds are generally more
  challenging to learn than different sounds for both chidlren (Stager
  and Werker, 1997) and adults (Pajak et al. 2016).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
  when the noise characterized with \(\sigma\) decreases. This fact may
  explain development, i.e., youger children have noisier
  representations (Swingley, 2007; Yoshida et al. 2009), which lead to
  lower word recognition accuracy, especially for similar sounding
  words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
  when the visual distance between the semantic referents \(\Delta o\)
  increases. This is a new predcition that our model makes. Previous
  work studied the effect of several bottom-up and top-down properties
  in disambiguating similar sounding words (see introduction), But no
  previous study tested the effect of the visual distance between the
  semantic referents.
\end{enumerate}

To sum, we introduced a model that accounts for some qualitative
patterns observed in previous studies, and makes new predictions. In the
experiment below, we test whether the model makes accurate
\emph{quantitative} predictions by fitting it to new experimental data
collected from preschool chidlren and adults.

{\centering \includegraphics{figs/illus-1}

\caption{\label{fig:illus}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters.}\label{fig:illus}
\end{figure}
\end{CodeChunk}

\section{Experiment}\label{experiment}

In this experiment, we tested participants in the word learning task
introduced above (Figure 1). We explored all three parameters of the
model. Both the sound similarity (\(\Delta s\)) and object similarity
(\(\Delta o\)) were varied simulataneousely in a within-subject design.
Besides, two age groups (preschool children and adults) were tested on
the same task to explore whether development can be characteized with
the degree of uncertainty, \(\sigma\), in the probabilsitic
representations.

We planned to recruit a sample of 60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. So far, we
collected data from N=47 children (mean age= months, F=). An additional
28 children participated but were removed from analyses because they
were not above chance on the catch trials (as was specified in the
pre-registration\footnote{https://osf.io/jrh38/}). We also collected a
planed sample of N=30 adults on Amazon Mechanical Turk. N=2 adult
participants were excluded because of low scores on the catch trials
(see pre-registration).

\subsubsection{Stimuli and similarity
rating}\label{stimuli-and-similarity-rating}

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit et al., 1996). We generated three kinds of sound pairs which
varied in their degree of similarity to English speakers: 1)
``different'': ``lif''/``neem'' and ``zem''/``doof'', 2)
``intermediate'': ``aka''/``ama'' and ``ada''/``aba'', and 3)
``similar'' non-English minimal pairs: ``ada''/``a\textipa{d\super h}a''
(in hindi) and ``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).

As for the objects, we used the Dynamic Stimuli javascript
library\footnote{https://github.com/erindb/stimuli} which allowed us to
generate objects in four different categories: ``tree'', ``bird'',
``bug'', and ``fish''. These categories are supposed to be naturally
occuring kinds that might be seen on an alien planet. In each category,
we generated ``different'', ``intermediate'' and ``similar'' levels of
similarity by manipuating a continuous property controling features of
the category's shape (e.g, body strech and head fatness).

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and objcet pair
on a 7-point scale. We used the average ratings across participants as
qunatitaive measures of sound pairs' distance (\(\Delta s\)) and object
pairs' distance (\(\Delta o\)).

Each age group saw only two of the three levels of similarity described
in the previous sub-section: ``different'' vs. ``intermediate'' for
preschoolers, and ``intermediate'' vs. ``similar'' for adults. The
experiment consisted of four conditions which involved, each, one pair
of sounds-objects associations. These conditions were constructed by
crossing the sound's degree of similarity with the object's degree of
similarity leading to a 2x2 factorial design in each age group. Besides
the 4 conditions, we also tested participants on a fifth catch condition
which was similar in its stucture to the other ones, but was used only
to select participant who were able to follow the instructions and show
minimal learning.

@@

Preschoolers were asked if they would be willing to play a game on a
tablet with the experimenter and were informed that they could stop
playing at any time. The experimenter explained that the game consisted
in learning some words spoken in an alien planet. The experiment began
with two simple examples (not included in the analysis), and in these
examples children were given feedback from the experimenter so as to
make sure they correctly understood the structure of the task. After the
introduction and examples, children were tested in a sequence of five
conditions: the four experimental conditions plus the catch condition.
In each condition, participants saw a first block of four exposure
trials followed by four testing trials, and a second block of two
exposure trials (for memory refreshment) follwoed by an additional four
testing trials.

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial.

The procedure for preschoolers and adults were identical except that
preschoolers were accompagnied by an experimenter and used a tablet,
whereas adults used their local computers to complete the experiment
online.

\subsubsection{Model fitting}\label{model-fitting}

We fit the analystical expression (equation 2) to the participants'
responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
were set based on data from the similarity judgment task (described in
the stimuli sub-section). We used two models: \textbf{model 1} fit only
one parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2}
fit two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
parameters were derived using weighted least-squares estimates.

\subsection{Results}\label{results}

First we analyzed the experimental results shown in Figure (XX, left),
using a mixed-effects logistic regression with sound and object
distances as fixed effects, and with a maximal random effects strcuture
(Barr et al. 2013). Results are shown in Table XX. We found a main
effect of sound distance on the accuray of learning in both children and
adults, thus replicating previous findings. We also found a main effect
of object distance, thus confirming the new hypothesis derived from our
model.

\begin{table}[!htbp] \centering 
  \caption{Estimates of predictor coefficients (and their standard errors) by age group in the regression model} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline \\[-1.8ex] 
 & Children & Adults \\ 
\hline \\[-1.8ex] 
 (Intercept) & 0.426$^{*}$ (0.199) & 3.114$^{**}$ (1.015) \\ 
  Sound  & 0.272$^{**}$ (0.100) & 2.320$^{*}$ (0.981) \\ 
  Object & 0.315$^{*}$ (0.137) & 2.133$^{*}$ (0.952) \\ 
  Sound x Object & 0.151 (0.097) & 1.821 (0.976) \\ 
 \hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.05; $^{**}$p$<$0.01; $^{***}$p$<$0.001} \\ 
\end{tabular} 
\end{table}
